\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sabuhi Teymurov} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+994(77)-740-16-00 \\ Sumqayit, Azerbaijan} 
\address{\href{mailto:hello@sabuhiteymurov.com}{hello@sabuhiteymurov.com} \\ \href{https://www.linkedin.com/in/sabuhi-teymurov/}{linkedin.com/in/sabuhi-teymurov} \\ \href{www.sabuhiteymurov.com}{www.sabuhiteymurov.com}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Results-driven software developer with 2+ years of experience developing and maintaining software
applications. Driven to continuously improve my technical skills and eager to work on
challenging projects that will help me expand my skill set.}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Javascript, Typescript
\\
Frameworks and Technologies & React, Next.js, React native, Redux, Node.js, NextAuth.js, Socket.IO,\\ & RTK Query, OAuth, MongoDB, Sass, Jest, Docker \\
Soft Skills & Adaptability, Collaboration, Communication, Time management, Empathy\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Front-End Developer} \hfill Aug 2022 - Present\\
Ferrum Capital \hfill \textit{Baku, Azerbaijan}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Collaborated with cross-functional teams, including product management and design, to deliver high-quality and user-friendly software.
     \item Mentored junior developers and provided technical guidance, leading to improved performance and knowledge retention.
    \item 
    Improved application performance by optimizing the codebase, reducing the number of re-renders through the utilization of libraries like react-hook-form. Additionally, caching techniques were implemented by incorporating technologies like React Query and RTK Query for further enhancing performance.
    \item Enhanced app performance by creating an infinite scrollable table capable of handling more than 200,000 data entries with the help of the tanstack/react-table, tanstack/react-virtual libraries and tanstack/react-query's useInfiniteQuery. 
    \item Utilized React Native (Expo framework) to develop cross-functional native apps for Android and iOS platforms. 
 \end{itemize}
 
\textbf{Junior Front-End Developer} \hfill Nov 2021 - Sep 2022\\
Freelancer.com \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Collaborated with clients to oversee the production and maintenance of website and web application interfaces, and developed reusable code for future use.
     \item Ensured that the front end of the websites was error-free and bug-free.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{
Kalee - Appointment Scheduling App} {Kalee is a software application designed to help individuals manage their appointments and schedules. It provides a convenient way to schedule and book appointments online, eliminating the need for manual appointment scheduling. Over 1000 people have used it so far, with 5000+ meetings being scheduled! \href{https://demo.kalee.app/}{(Project link)} \begin{itemize}
    \itemsep -3pt {} \item Led the project's front end, which included the development and implementation of the app from scratch.
    \item Implemented a real-time appointment booking system with the help of the Socket.IO client, enabling users to view available times.
   \item Integrated and prepared the app for verification on Google Meets, Zoom, and Microsoft Teams platforms. Implemented authentication and authorization for the app (sign-in/sign-up/JWT refresh token strategy) using technologies such as Axios interceptors and the NextAuth.js library. \end{itemize}}
\item \textbf{
    Ferrum Capital Corporate Website} {The main technologies utilized were jQuery, CSS, and Laravel blade templates. API integration and validation across the entire website. The website is regularly tested with Google Lighthouse for usability, speed, and other quality factors. Ensured the website is accessible across many platforms, including devices using older versions of macOS and iOS. \href{https://ferrumcapital.az}{(Project link)}}
\end{rSection} 

%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
%     \item	Sample bullet point.
% \end{itemize}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    
    {\bf Bachelor of Management}, Azerbaijan Tourism and Management University \hfill {2017 - 2021}
    %Minor in Linguistics \smallskip \\
    %Member of Eta Kappa Nu \\
    %Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}


% \end{rSection}


\end{document}